---
title: "p8105_hw1_yy3563"
author: "Yifei Yu"
date: "2024-09-20"
output: github_document
---

### Problem 1

## Load the penguins dataset.

```{r}
library(palmerpenguins)
data("penguins", package = "palmerpenguins")
```

The `penguins` dataset includes data on `species`, `island`, `bill_length_mm`, `bill_depth_mm`, `flipper_length_mm`, `body_mass_g`, `sex`, and `year` of penguins from three different species: Adelie, Gentoo, and Chinstrap. 

The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns. 

The mean flipper length of the penguins is `r mean(penguins$flipper_length_mm, na.rm = TRUE )` mm.

## Make the scatterplot and export to project directory.

```{r}
library(tidyverse)

plot_penguin = tibble(
  x = penguins$bill_length_mm,
  y = penguins$flipper_length_mm,
  species = penguins$species
)

ggplot(plot_penguin, aes(x = x, y = y, color = species)) + 
  geom_point() +
  labs(x = "bill length (mm)", y = "flipper length (mm)", color = "species")

ggsave("scatter_penguin.pdf", height = 4, width = 4 )
```


### Problem 2

## Create the dataframe.

```{r}
df = tibble(
  random_sample = rnorm(10),
  logical_vector = rnorm(10) > 0,
  character_vector = character(10),
  factor_vector = factor(rep(c("Level1", "Level2", "Level3"), length.out = 10))
)
```

## Take the means using pull function.

```{r}
mean_random_sample = mean(pull(df, random_sample))
mean_logical_vector = mean(pull(df, logical_vector))
mean_character_vector = mean(pull(df, character_vector))
mean_factor_vector = mean(pull(df, factor_vector))
```

## Write a code chunk that applies the as.numeric function to the logical, character, and factor variables

```{r}
logical_numeric = as.numeric(df$logical_vector)
character_numeric = as.numeric(df$character_vector)
factor_numeric = as.numeric(df$factor_vector)
```

When calculating mean for character and factor variables, there will be an error. After using the as.numeric function, the character and factor variables turned into numeric version, and then we can get the mean of them. 