---
title: "p8105_hw1_yy3563"
author: "Yifei Yu"
date: "2024-09-20"
output: github_document
---

### Problem 1

## Load the penguins dataset.

```{r}
library(palmerpenguins)
data("penguins", package = "palmerpenguins")
```

The `penguins` dataset includes data on `species`, `island`, `bill_length_mm`, `bill_depth_mm`, `flipper_length_mm`, `body_mass_g`, `sex`, and `year` of penguins from three different species: Adelie, Gentoo, and Chinstrap. 

The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns. 

The mean flipper length of the penguins is `r mean(penguins$flipper_length_mm, na.rm = TRUE )` mm.

## Make the scatterplot and export to project directory.

```{r}
library(tidyverse)

plot_penguin = tibble(
  x = penguins$bill_length_mm,
  y = penguins$flipper_length_mm,
  species = penguins$species
)

ggplot(plot_penguin, aes(x = x, y = y, color = species)) + 
  geom_point() +
  labs(x = "bill length (mm)", y = "flipper length (mm)", color = "species")

ggsave("scatter_penguin.pdf", height = 4, width = 4 )
```

